---
title: "Analyses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = F,
                      warning = F)
library(tidyverse)
library(patchwork)
```

## read the data

```{r}
df_aic <- read_csv("result_aic.csv")
df_lasso <- read_csv("result_lasso.csv")
```


## Making Tables and Plots for AIC Method

### Simple Tables

#### overall summary statistics

```{r}
df_aic %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
  ) %>% 
  knitr::kable(caption = "The Overall Performance of AIC Method")
```

#### Summary by Method

```{r}
df_aic %>% 
  group_by(method) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of AIC Method by Simulation Method")
```


#### summary by number of predictor p

```{r}
df_aic %>% 
  group_by(p) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of AIC Method by Number of Predictors")
```

#### summary by correlation
```{r}
df_aic %>% 
  group_by(corr) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of AIC Method by Correlation")
```

#### summary by design of beta

```{r}
df_aic %>% 
  group_by(beta) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of AIC Method by Beta Design")
```

#### summary by proportion of different signals

```{r}
df_aic %>% 
  mutate(signal_design = c(rep(1,7200),rep(2,7200))) %>% 
  group_by(signal_design) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of AIC Method by Proprtion of Signals")
  
```

### Corss-wise Tables:

#### beta design + correlation

```{r}
df_aic %>% 
  group_by(beta,corr) %>% 
  summarize( 
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of AIC Method By Beta Design and Correlation")
# intersting!
```

#### signal design + correlation

```{r}
df_aic %>% 
  mutate(signal_design = c(rep(1,7200),rep(2,7200))) %>% 
  group_by(signal_design,corr) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of AIC Method By Signal Design and Correlation")
# do not interest 
```


#### number of predictor + corr

```{r}
df_aic %>% 
  group_by(corr,p) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of AIC Method By Number of Predictors and Correlation")

# not interesting
```

## Plots

### prop vs number of predictors 

```{r}
  df_aic %>% 
  group_by(p) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
)  %>% 
  pivot_longer(
    avg_s1_prop:avg_s3_prop,
    names_to = "signals",
    values_to = "avg_proportion"
  ) %>% 
    separate(signals, sep= "_", into = c("avg","signal","prop")) %>% select(-avg, - prop) %>% 
  ggplot(aes(x = p, y = avg_proportion, color = signal)) + 
  geom_line() +
  theme_minimal() +
  labs(y = "Average TP Rate", 
       x = "Number of Predictors", 
       title = "AIC") +
  theme(text = element_text(size=16))
   
```

### prop vs p + method

```{r}
  df_aic %>% 
  group_by(method, p) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
)  %>% 
  pivot_longer(
    avg_s1_prop:avg_s3_prop,
    names_to = "signals",
    values_to = "avg_proportion"
  ) %>% 
    separate(signals, sep= "_", into = c("avg","signal","prop")) %>% select(-avg, - prop) %>% 
  mutate(method = as.factor(method)) %>% 
  ggplot(aes(x = p, y = avg_proportion, color = method)) + 
  geom_line() +
  facet_wrap(.~signal,scales = "free")+
  labs(y = "Average TP Rate", 
       x = "Number of Predictors", 
       title = "AIC") +
   theme(axis.text=element_text(size=14),
        axis.title=element_text(size=10)) +
  theme_minimal() +
  theme(text = element_text(size=16))
```

### prop vs corr + beta

```{r}
  df_aic %>% 
  group_by(corr, beta, method) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
)  %>% 
  pivot_longer(
    avg_s1_prop:avg_s3_prop,
    names_to = "signals",
    values_to = "avg_proportion"
  ) %>% 
    separate(signals, sep= "_", into = c("avg","signal","prop")) %>% select(-avg, - prop) %>% 
  #mutate(corr = as.factor(corr)) %>% 
  ggplot(aes(x = corr, y = avg_proportion, color = beta)) + 
  geom_line() +
  facet_grid(method~signal, scales = "free_y")+
  labs(y = "Average TP Rate", 
       x = "Correlation", 
       title = "AIC")+
   theme_minimal() +
  theme(text = element_text(size=16))
```
```

## Making Tables and Plots for Lasso Method

### Simple Tables

#### overall summary statistics

```{r}
df_lasso %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
  ) %>% 
  knitr::kable(caption = "The Overall Performance of Lasso Method")
```

#### Summary by Method

```{r}
df_lasso %>% 
  group_by(method) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of Lasso Method by Simulation Method")
```


#### summary by number of predictor p

```{r}
df_lasso %>% 
  group_by(p) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of Lasso Method by Number of Predictors")
```

#### summary by correlation

```{r}
df_lasso %>% 
  group_by(corr) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of Lasso Method by Correlation")
```

#### summary by design of beta

```{r}
df_lasso %>% 
  group_by(beta) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of Lasso Method by Beta Design")
```

#### summary by proportion of different signals

```{r}
df_lasso %>% 
  mutate(signal_design = c(rep(1,7200),rep(2,7200))) %>% 
  group_by(signal_design) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of Lasso Method by Proprtion of Signals")
  
```

### Corss-wise Tables:

#### beta design + correlation

```{r}
df_lasso %>% 
  group_by(beta,corr) %>% 
  summarize( 
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of Lasso Method By Beta Design and Correlation")
# intersting!
```

#### signal design + correlation

```{r}
df_lasso %>% 
  mutate(signal_design = c(rep(1,7200),rep(2,7200))) %>% 
  group_by(signal_design,corr) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of Lasso Method By Signal Design and Correlation")
# do not interest 
```


#### number of predictor + corr

```{r}
df_lasso %>% 
  group_by(corr,p) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
) %>% 
  knitr::kable(caption = "The Performance of Lasso Method By Number of Predictors and Correlation")

# not interesting
```

## Plots

### prop vs number of predictors 

```{r}
df_lasso %>% 
  group_by(p) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
)  %>% 
  pivot_longer(
    avg_s1_prop:avg_s3_prop,
    names_to = "signals",
    values_to = "avg_proportion"
  ) %>% 
    separate(signals, sep= "_", into = c("avg","signal","prop")) %>% select(-avg, - prop) %>% 
  ggplot(aes(x = p, y = avg_proportion, color = signal)) + 
  geom_line() +
  labs(y = "Average TP Rate", 
       x = "Number of Predictors", 
       title = "Lasso") +
    theme_minimal() +
  theme(text = element_text(size=16))
```
```

### prop vs p + method

```{r}
df_lasso %>% 
  group_by(method, p) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
)  %>% 
  pivot_longer(
    avg_s1_prop:avg_s3_prop,
    names_to = "signals",
    values_to = "avg_proportion"
  ) %>% 
    separate(signals, sep= "_", into = c("avg","signal","prop")) %>% select(-avg, - prop) %>% 
  mutate(method = as.factor(method)) %>% 
  ggplot(aes(x = p, y = avg_proportion, color = method)) + 
  geom_line() +
  facet_wrap(.~signal,scales = "free")+
  labs(y = "Average TP Rate", 
       x = "Number of Predictors", 
       title = "Lasso") +
    theme_minimal() +
  theme(text = element_text(size=16))
```
```

### prop vs corr + beta

```{r}
df_lasso %>% 
  group_by(corr, beta, method) %>% 
  summarize(
    avg_s1_prop = mean(s1_prop),
    avg_s2_prop = mean(s2_prop),
    avg_s3_prop = mean(s3_prop)
)  %>% 
  pivot_longer(
    avg_s1_prop:avg_s3_prop,
    names_to = "signals",
    values_to = "avg_proportion"
  ) %>% 
    separate(signals, sep= "_", into = c("avg","signal","prop")) %>% select(-avg, - prop) %>% 
  #mutate(corr = as.factor(corr)) %>% 
  ggplot(aes(x = corr, y = avg_proportion, color = beta)) + 
  geom_line() +
  facet_grid(method~signal, scales = "free_y") +
  labs(y = "Average TP Rate", 
       x = "Correlation", 
       title = "Lasso") +
   theme_minimal() +
  theme(text = element_text(size=16))
```






